Uncovering underlying high-level musical content in the time domain \\ \small Leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn deep audio embeddings with applications to MIR downstream tasks

### 2023-06-09 introduction/Subsections/Previous work.tex
Updates from Overleaf

Neural networks have recently facilitated the development of low-dimensional embeddings that capture essential musical features, enabling the computation of various task-specific aspects.

These aspects include the utilization of multi-level music segmentation through deep audio embeddings to replace manually engineered features \cite{SalamonDeepSegmentation}, the enhancement of environmental sound classification \cite{Kim2020OneStrategies}, the improvement of vocal-centric music tasks using cross-domain audio embedding \cite{Kim2021LearningLoss}, the enhancement of audio classification through a combination of task-specific and pre-trained features \cite{Hung2022Feature-informedClassification}, the creation of a music similarity search engine specifically for video producers \cite{epidemic}, the improved performance in Music Emotion Recognition (MER) tasks \cite{KohComparisonRecognition}, embedding songs for similarity comparison based on artist identification \cite{contentmusicsimtriplet2020}, the resolution of the cross-modal text-to-music retrieval problem \cite{WonEmotionStories}, and automated music rearrangement \cite{Stoller2018IntuitiveTransitions}\cite{Plachouras2023MusicSegmentation}.

On top of that and returning to musicological influences, the middle ground in Schenkerian analysis can be compared to the mesostructure in music. Analogous to the mesostructure, it represents the intermediate-level musical patterns that bridge the micro and macro structures. This element is often overlooked when applying deep learning to music. As emphasized by \cite{Mesostructures2023}, models that address this mesostructure level could significantly enrich tasks such as music analysis, composition, and retrieval, providing a more holistic understanding of music, similar to the insights gained from analyzing the middle-ground in Schenkerian analysis. \cite{Introduction_to_Schenkerian_Analysis}

Moreover, deep audio embeddings offer the advantage of transferability. Once trained, these latent representations can be utilized as a starting point for various other tasks, thus saving computational resources and time compared to training a model from scratch \cite{HamelTransferSimilarity}.

Given their demonstrated success in the literature and their potential for transfer learning, exploring deep audio embeddings for MIR downstream tasks seems worthwhile.

>>>>

Previous studies have highlighted the significance of selecting suitable audio features to distinguish and label unique music segments in music segmentation tasks. However, acquiring music segment annotation data for learning feature transformations presents a challenge due to its labor-intensive and expensive nature. Research has leveraged unsupervised deep learning to mitigate this, using readily available music audio. This methodology has significantly enhanced the efficacy of segmentation algorithms, yielding state-of-the-art results. Furthermore, strategies that recognize the hierarchical nature of the structural organization employing two-level annotations of primary and secondary boundaries have further augmented boundary detection performance \cite{unsupervisedlearndeepfeat, GrillMUSICANNOTATIONS, Hernandez-Olivan2021MusicFeatures, SalamonDeepSegmentation}.

Apart from music structure applications, recent advances in neural networks have facilitated the generation of low-dimensional numerical representations that encapsulate key musical attributes. This development simplifies the computation of various task-specific elements. Such tasks encompass:

\begin{itemize}
\item Developing an audio embedding method that excels across numerous applications without the need for fine-tuning \cite{Turian2022HEAR:Representations}
\item Enhancing environmental sound classification \cite{Kim2020OneStrategies, CramerLOOKEMBEDDINGS}
\item Improving vocal-centric music tasks via cross-domain audio embeddings \cite{Kim2021LearningLoss}
\item Merging task-specific and pre-trained features to improve audio classification \cite{Hung2022Feature-informedClassification}
\item Designing a music similarity search engine for video producers \cite{epidemic}
\item Augmenting Music Emotion Recognition (MER) performance \cite{KohComparisonRecognition}
\item Investigating the efficacy of speaker recognition pre-trained model embeddings \cite{lightweight}
\item Embedding songs for similarity comparison via artist identification \cite{contentmusicsimtriplet2020}
\item Addressing the cross-modal text-to-music retrieval issue \cite{WonEmotionStories}
\item Facilitating automated music rearrangement \cite{Stoller2018IntuitiveTransitions, Plachouras2023MusicSegmentation}
\end{itemize}

Moreover, deep audio embeddings provide the advantage of transferability, serving as a basis for multiple tasks. This approach conserves computational resources and time compared to training a model from scratch \cite{HamelTransferSimilarity}.

Given their demonstrated effectiveness in existing literature and their potential for transfer learning, deep audio embeddings hold substantial promise for MIR downstream tasks, specifically boundary detection. Nevertheless, it remains uncertain whether a general-purpose audio representation can effectively replicate human hearing \cite{Turian2022HEAR:Representations}, even though some techniques have managed to generalize across up to fourteen music understanding tasks \cite{Li2023MERT:Training}.

### 2023-06-09 methods/subsections/implementation.tex
Updates from Overleaf

Our approach could be broadly categorized as cognitive modeling, as it strives to mimic human cognitive processes and problem-solving through a computerized model. We champion exposure-based learning in music and active engagement with musical styles, genres, techniques, and learning methods to foster well-rounded musical proficiency and efficient performance with novel data in practical applications.

\subsection{Contrastive Learning of Musical Representations}

Piaget's theory of cognitive development suggests children acquire knowledge through sensory experiences, gradually developing abstract reasoning and schemas—basic cognitive structures \cite{Huitt2003PiagetsDevelopment}. These schemas evolve by integrating new information through assimilation and accommodation \cite{audioselfsupsurvey}.

In pattern recognition, models are designed to be robust against known invariances—input data transformations—allowing consistent output. Conversely, unknown invariances not considered in the model's design can still be handled due to its learning capacity.

Contrastive Learning of Musical Representations (CLMR) learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones \cite{CLMR2021}. CLMR works under a machine learning subset called self-supervised learning (SSL), where models self-learn from unlabeled data, creating their supervisory signal \cite{audioselfsupsurvey}. This mimics human learning from observations and interactions, transforming unsupervised problems into supervised ones by auto-generating labels. The benefits of SSL include reduced reliance on labeled data, making data representation more robust and generalizable.

The CLMR methodology involves creating different augmentations of the same musical piece as positive pairs and using others as antagonistic pairs. Then, training by minimizing a contrastive loss function encourages the model to produce similar representations for positive pairs and dissimilar representations for antagonistic pairs.

Although SSL has been proven effective in speech and audio, its
application to music audio has yet to be thoroughly explored. This is primarily due
to the distinctive challenges associated with modeling musical knowledge, particularly tonal and pitched characteristics of music \cite{Li2023MERT:Training}.

@@

\textbf{Amplitude effects}, like gain, modify the signal's amplitude with a constant factor $g$. We use $g \in [-12, 0]$.

>>>>

Our approach falls broadly under cognitive modeling, which seeks to simulate human cognitive processes and problem-solving through a computerized model. We advocate for exposure-based learning in music, encouraging active engagement with various musical styles, genres, techniques, and learning methods. This approach promotes comprehensive musical proficiency and efficient performance when encountering novel data in practical applications.

According to Piaget's theory of cognitive development, children gain knowledge through sensory experiences and gradually develop abstract reasoning and schemas—basic cognitive structures \cite{Huitt2003PiagetsDevelopment}. These schemas evolve by incorporating new information through processes of assimilation and accommodation \cite{audioselfsupsurvey}.

In pattern recognition, models are designed to exhibit robustness against known invariances—transformations of input data—thereby ensuring consistent output. Interestingly, even unknown invariances not explicitly considered in the model's design can be accommodated due to the model's inherent learning capacity.

Contrastive Learning of Musical Representations (CLMR) is a method that learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones \cite{CLMR2021}. CLMR falls under a subset of machine learning called self-supervised learning (SSL) \cite{Balestriero2023ALearning}, where models learn independently from unlabeled data to create their supervisory signals \cite{audioselfsupsurvey}. This method resembles how humans learn from observations and interactions, turning unsupervised problems into supervised ones by auto-generating labels. Benefits of SSL include reduced dependence on labeled data, which contributes to more robust and generalizable data representations.

The methodology of CLMR involves generating different augmentations of the same musical piece to serve as positive pairs while using other pieces as antagonistic pairs. The training process, which minimizes a contrastive loss function, encourages the model to produce similar representations for positive and dissimilar ones for antagonistic pairs.

Although SSL has proven effective in speech and audio, its application to music audio remains relatively unexplored. This is primarily due to the unique challenges associated with modeling musical knowledge, especially when it comes to music's tonal and pitched characteristics \cite{Li2023MERT:Training}.

@@

\textbf{Amplitude effects}, we use gain to modify the signal's amplitude with a constant factor $g \in [-12, 0]$.
